Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-31 paper/paper.tex
minor fixes on methodology

We describe the methodology we used in this experiment in the
following. Recall that our tool produces warnings on output organized
in buckets (Section~\ref{sec:design}). Each bucket describes a
warnings--one per file (fuzzed or not)--and can be of ``lo'' or ``hi''
importance, according to the heuristic we
defined. Figure~\ref{fig:distribution} shows the distribution of
warnings reported per bucket. Observe that in some cases the number of
files per bucket is very high; it would be infeasible to manually
inspect all of them. For that, we inspected each and every reported
bucket but only one file per bucket. For the cases we found
suspicious, we filed a bug report in the bug tracker. In some cases,
we used the Mozila lithium tool~\cite{lithium} to minimize the test
case. Table~\ref{tab:summary-of-results} summarizes the number of
buckets of each category per execution mode. \Fix{elaborate}

>>>>

We describe the methodology we used in this experiment in the
following. Recall that our tool produces warnings on output organized
in buckets (Section~\ref{sec:design}). Each bucket includes a set of
warnings and each warning is related to one file.  A bucket is of
``lo'' or ``hi'' importance, according to the heuristic we
defined. Figure~\ref{fig:distribution} shows the distribution of
warnings reported per bucket. Observe that, in some cases, the number
of files per bucket is very high; it would be impractical to manually
inspect all of them. For that, we inspected each and every bucket but
only inspected one file per bucket. For the cases we found the warning
suspicious, we analyzed the parts of the documentation related to the
problem and, if still suspicious, we looked on the bug tracker of the
affected engine for potential duplicates. If none was reported, we
filed a bug report in the bug tracker including the test input that
manifested the potential problem and explaining the reasons we were
suspicious. In some cases, we used the Mozila lithium
tool~\cite{lithium} to minimize the test case. For the cases of false
positive warnings, we classified the reason and moved to the next
bucket. Table~\ref{tab:summary-of-results} summarizes the number of
buckets of each category per execution mode. \Fix{elaborate}
